%!TEX root= cvFioretto.tex
%Section: Scholarships and additional info
\sectionTitle{Teaching}{}%{\faMortarBoard}

% \begin{experiences}
%   \teach
%     {Spring 2021} {Security and Privacy of Machine Learning (CS 700)}{Syracuse University}
%     {4.93/5.00 (median 5.00)}
%   \teach
%     {Fall 2021} {Introduction to Artificial Intelligence (CIS 467)}{Syracuse University}
%     {4.38/5.00 (median 5.00)}
%   \teach
%     {Spring 2021} {Security and Privacy of Machine Learning (CS 700)}{Syracuse University}
%     {4.46/5.00 (median 5.00)}
%   \teach
%     {Fall 2020} {Introduction to Artificial Intelligence (CIS 467)}{Syracuse University}
%     {4.56/5.00 (median 5.00)}
%   \teach
%     {Spring 2020} {Security and Privacy of Machine Learning (CS 700)}{Syracuse University}
%     {4.55/5.00 (median 5.00)}
% \end{experiences}


\begin{experiences}
  \multicolumn{2}{l}{\textbf{Responsible AI (CS 7000)}, 
                         \textit{University of Virginia}}\\[0.35em]
  \textbf{Spring 2024} & \textsc{Course Evaluation: } {4.8 (class), 4.82 (instructor) / 5.00}\\[0.35em]

  \multicolumn{2}{l}{\textbf{Artificial Intelligence (CS 4710)}, 
                         \textit{University of Virginia}}\\[0.35em]
  \textbf{Fall 2023} & \textsc{Course Evaluation: } {4.33 (class), 4.5 (instructor) / 5.00}\\[0.35em]

  \multicolumn{2}{l}{\textbf{Security and Privacy of Machine Learning (CS 700)}, 
                         \textit{Syracuse University}}\\[0.35em]
  \textbf{Spring 2020} & \textsc{Course Evaluation: } {4.55/5.00 (median 5.00)}\\[0.35em]
  \textbf{Spring 2021} & \textsc{Course Evaluation: } {4.46/5.00 (median 5.00)}\\[0.35em]
  \textbf{Spring 2022} & \textsc{Course Evaluation: } {4.93/5.00 (median 5.00)}\\
  \emptySeparator

  \multicolumn{2}{l}{\textbf{Introduction to Artificial Intelligence (CIS 467)}, 
                         \textit{Syracuse University}}\\[0.35em]
  \textbf{Fall 2020} & \textsc{Course Evaluation: } {4.56/5.00 (median 5.00)}\\[0.35em]
  \textbf{Fall 2021} & \textsc{Course Evaluation: } {4.48/5.00 (median 5.00)}\\[0.35em]
  \textbf{Fall 2022} & \textsc{Course Evaluation: } {4.45/5.00 (median 5.00)}\\[0.35em]
  \textbf{Fall 2023} & \textsc{Course Evaluation: } {4.15/5.00 (median 5.00)}\\
  \emptySeparator

  \multicolumn{2}{l}{\textbf{Discrete Mathematics (CS 375)}, 
                         \textit{Syracuse University}}\\[0.35em]
   \textbf{Spring 2023} & \textsc{Course Evaluation: } {4.60/5.00 (median 5.00)}\\[0.35em]

\end{experiences}

\sectionTitle{Mentoring}{}%{\faGroup}
\medskip

\subsection*{Current PhD Students}
\begin{itemize}
  \item \textbf{James Kotary} ({\sc UVA}, CS) 
  \hfill{\em Fall 2020 -- current}\\
  {\sc Research}: Integration of Deep Learning and Optimization.
  %Current Position: \textit{Same}

  \item \textbf{Vincenzo Di Vito} ({\sc UVA} CS)
  \hfill{\em Fall 2022 -- current}\\
  {\sc Research:} Physics Informed Machine Learning.
  
  \item \textbf{My Dinh} ({\sc UVA} CS) 
  \hfill{\em Spring 2021 -- current}\\
  {\sc Research}: Deep Learning, Optimization, Fairness.
  %Current Position: \textit{Same}

  \item \textbf{Saswat Das} ({\sc UVA} CS)
  \hfill{\em Fall 2023 -- current}\\
  {\sc Research:} Responsible AI, Differential Privacy.

  \item \textbf{Jacob K.~Christopher} ({\sc UVA} CS)
  \hfill{\em Fall 2023 -- current}\\
  {\sc Research:} Responsible AI in Generative Models.

  \item \textbf{Jinhao Liang} ({\sc UVA} CS)
  \hfill{\em Fall 2024}\\
  {\sc Research:} Differentiable Optimization.

  \item \textbf{Michael Cardei} ({\sc UVA} CS)
  \hfill{\em Fall 2024}\\
  {\sc Research:} Responsible Generative AI.

  \item \textbf{Joseph Moretto} ({\sc UVA} CS)
  \hfill{\em Fall 2024}\\
  co-advised with David Evans\\
  {\sc Research:} Responsible Generative AI.
\end{itemize}

\subsection*{Past (Graduated) Students}
\begin{itemize}
  \item \textbf{Cuong Tran} ({\sc PhD, Syracuse University}, CISE) 
  \hfill{\em Spring 2020 -- Spring 2023}\\
  {\sc Research}: Differential Privacy and Fairness.\\
  {\sc Dissertation Title:} The Interplay between Privacy and Fairness in
  Learning and Decision-making Problems\\
  {\sc Next position:} Research Scientist, Amazon.

  \item \textbf{Jacob Kennedy Christopher} ({\sc MS, Syracuse University}) \hfill{\em Spring 2023}\\
  {\sc Research:} Differentiable Optimiztion.\\
  {\sc Next position:} PhD student at \textit{University of Virginia}.

  \item \textbf{Yehya Farhat} ({\sc MS, Syracuse University}) \hfill{\em Fall 2022}\\
  {\sc Dissertation Title:} Surrogate ML models for optimization.\\
  {\sc Next position:} PhD student at \textit{Rice University}.

  % \item \textbf{Klaus Peng} ({\sc MS, University of Virginia}) \hfill{\em Fall 2023}\\
  % {\sc Research:} Causality.
\end{itemize}

\subsection*{Current MS and BS Students}
\begin{itemize}
  \item  \textbf{Joonhyuk Ko} ({\sc BS, UVA} CS)  \hfill{\em Fall 2023 -- current}
  \item  \textbf{Matthew Galitz} ({\sc BS, UVA} CS)  \hfill{\em Fall 2024}
  \item  \textbf{Jameson Sandler} ({\sc BS, UVA} CS)  \hfill{\em Fall 2024}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Other Advised Students and Visitors}
\begin{itemize}
  \item \textbf{Cuong Tran} ({\sc Postdoc}) 
  \hfill{\em Sep 2023 -- Mar 2024}\\
  {\sc Research}: Data Minimization, Fairness in Large Language Models.

  \item \textbf{Razan Tajeddine}, PhD at U of Helsinki ({\sc Visiting postdoc}) 
  \hfill{\em Sep 2023 -- Mar 2024}\\
  {\sc Research}: Differential Privacy and Fairness.

  \item \textbf{St John Grimbly}, MS at UniSA ({\sc Visiting Student Researcher}) 
  \hfill{\em Spring 2023}\\
  {\sc Next position:} PhD student at \textit{University of South Africa}.

  \item \textbf{Jayanta Mandi}, PhD at KU Leuven ({\sc Visiting Student Researcher}) 
  \hfill{\em Jun 2022 -- Sep 2022}\\
  {\sc Research}: Decision Focused Learning.

  \item \textbf{Rakshit Naidu}, MS at CMU ({\sc Intern}) \hfill{\em Summer 2022}\\
  {\sc Research:} Privacy and Fairness in ML. 
  {\sc Next position:} PhD student at \textit{Georgia Tech}
\end{itemize}

\subsection*{BS and High-School Students}
  \textbf{Shujun Xia} (BS, City University of Hong Kong, Summer 2024), 
  \textbf{Zarreen Reza} (BS, OpenMined, Spring 2024), 
  \textbf{Eric Nguyen} (BS, University of Virginia, Fall 2023),
  \textbf{Catherine Smolka} (HS, Deep Run High School, VA, 2023-2024), 
  %%
  \textbf{Pranav Putta} (BS, GaTech, Summer 2023) [NSF REU],
  \textbf{Winston Tsui} (BS, SU Summer 2023),
  \textbf{Zhongquan Cheng} (BS SU, Summer 2023), 
  %%
  \textbf{Adya Parida} (BS SU, Fall 2022) [NSF REU], 
  \textbf{Deniz Gursoy} (HS, Fayetteville High School, Summer 2022), 
  \textbf{Saswat Das} (BS, ITS, Summer 2022), 
  \textbf{Utsav Pathak} (BS, Alliance University, Bengaluru, Summer 2022),
  \textbf{Daiwei Shen} (BS, Northwestern, Summer 2022),
  \textbf{Sunisth Kumar} (BS, Bennett University, Summer 2022),
  %%
  \textbf{Kyle Beiter} (BS, SU, Summer 2021) [NSF REU],  %NSF REU
  \textbf{Shantanu Jhaveri} (BS, USC, Summer 2021) [NSF REU], % NSF REU
  \textbf{Dayong Gu} (BS, SU, Summer 2021),
  \textbf{Guoliang Chen} (BS, SU, Summer 2021),
  \textbf{Pradyumn Yadav} (BS, SU, Summer 2021),
  %%
  \textbf{Anudit Nagar} (BS, SU, Summer 2020 -- Current), 
  \textbf{Zhiyan Yao} (BS, SU, Summer 2020 -- Current),
  \textbf{Zifei Lu} (BS, SU, Summer 2020),
  \textbf{Thomas Montfort} (BS, SU, Summer 2020),
  \textbf{Cong Liu} (BS, SU, Summer 2020),
  \textbf{Pratik Paranjape}, (BS, SU, Summer 2020),
  % {\sc Research}: Generating datasets for preference elicitation. 
  % {\sc Next position:} \textit{Developer at OthersideAI}
  \textbf{Pavan Kumar Vaddineni} (BS, SU, Spring 2020),
  % {\sc Research}: Explainable and Fair Learning. 
  % {\sc Next position:} \textit{Same}
  \textbf{William Kluegel}, (BS, NMSU, 2016 -- 2018), 
  % {\sc Research}: \textit{Optimization and Preferences Elicitation for Smart Home Devices.}
  % {\sc Next position:} \textit{Sandia National Labs}
  \textbf{Lyndon Shi} (BS, UMich, 2018), 
  \textbf{Jiayu Chen} (BS, UMich, 2018), 
  \textbf{Eric Frechette} (BS, NMSU, 2016).
\medskip

\subsection*{PhD Dissertation Committee}
\begin{itemize}
  \item \textbf{Guangtao Zheng}, ({\sc University of Virginia}) \hfill 2024
  \item \textbf{Dung Nguyen}, ({\sc University of Virginia}) \hfill 2023
  \item \textbf{Elena Long}, ({\sc University of Virginia}) \hfill 2023
  \item \textbf{Khang Tran}, ({\sc New Jersey Institute of Technology}) \hfill 2023
  \item \textbf{Keyu Zhu}, ({\sc Georgia Institute of Technology}) \hfill 2023
  \item \textbf{Adrià Fenoy Barcel}, ({\sc University of Verona}) \hfill 2023
  \item \textbf{Jeroen Fransman}, ({\sc Delft University of Technology}) \hfill 2022
  \item \textbf{Pegah Hozhabrierdi}, ({\sc Syracuse University}) \hfill 2022
  \item \textbf{Carlos Pinzon}, ({\sc École Polytechnique}) \hfill 2022
  \item \textbf{Baocheng Geng}, ({\sc Syracuse University}) \hfill 2021
  \item \textbf{Pranay Sharma}, ({\sc Syracuse University}) \hfill 2021
\end{itemize}
\medskip