%!TEX root=cvFioretto.tex

\sectionTitle{Tutorials, Selected Invited Talks and Media interviews}{}%{\faTv}%{\faMicrophone}
\vspace{6pt}
\begin{itemize}
  \item {\bf Workshop talk}: On the Safety of Foundations Models for Autonomous BioLabs.
  \hfill {Feb 2024}\\
  \nemph{DOE Workshop on Envisioning Frontiers in AI and Computing for Biological Research}

  \item {\bf Keynote talk}: Privacy and Fairness issues in Large Language Models.
  \hfill {Nov 2024}\\
  \nemph{S-HPC Workshop, at Supercomputing 24}

  \item {\bf Invited talk}: Unfairness in Constrained Machine Learning.
  \hfill {Nov 2024}\\
  \nemph{Ohio State University, Department of Computer Science}

  \item {\bf Invited talk}: Constraining diffusion models for scientific applications.
  \hfill {Oct 2024}\\
  \nemph{UVA LLM Workshop}

  \item {\bf Invited talk}: Privacy and Fairness in Resource Allocations. \hfill{Oct 2024}\\
  \nemph{2024 Federal Committee on Statistical Methodology (FCSM) Research and Policy Conference}

  \item {\bf Invited talk}: Constrained Diffusion for Science and Engineering.\hfill {Oct 2024}\\
  \nemph{Oklahoma State University, School of Industrial Engineering and Management}

  \item {\bf Invited talk}: Constrained Diffusion for Science and Engineering.\hfill {Sep 2024}\\
  \nemph{University of Virginia, Department of Systems and Information Engineering}

  \item {\bf Podcast invited speaker}: 
  NSI Cyber and Tech Center: "Unleashing Innovation: Navigating Game Changing Technologies" -- episode on open source large language model.
  \hfill{Jul 2024}\\
  \nemph{National Security Institute at George Mason University's Antonin Scalia Law School}

  \item {\bf Invited participant and group lead}: 
  {US-UK Scientific Forum on Science in the Age of AI.} \hfill{Jun 2024}\\
  \press{https://www.nasonline.org/programs/scientific-forum/age-of-AI.html}{{\nemph{National Academy of Sciences}}}

  \item {\bf Panelist}: {AI and OR summer school.} \hfill{May 2024}\\
  \press{https://ai-score.github.io}{{\nemph{AI-SCORE}}}

  \item {\bf Invited talk}: Fairness in ML: The curious case of computational shortcuts and hardware choices. \hfill{May, 2024}\\
  \press{https://www.youtube.com/watch?v=WjJ40BU31vw}{{\nemph{BuzzRobot}}}

  \item {\bf Invited talk}: The Principle of Data Minimization in Machine Learning. \hfill{Apr, 2024}\\
  {\nemph{Google Research Seminars}}

  \item {\bf Media cover}: 
  {Building fairness into AI is crucial – and hard to get right.} \hfill {Mar 2024} \\
  \press{https://theconversation.com/building-fairness-into-ai-is-crucial-and-hard-to-get-right-220271}{{\nemph{The Conversation}}}, 
  \press{}{CHED/QR Radio}

  \item {\bf Invited talk}: Responsible AI in Decision Making Processes. \hfill{Feb 2024}\\
  {\nemph{Amazon Research Seminars}}
  
  \item {\bf Keynote talk}: {Privacy and Fairness in Societal Systems.} \hfill{Nov 2023}\\
  {\nemph{Workshop on the Tradeoffs in Ethical AI}, INRIA, France}

  \item {\bf Invited talk}: {Responsible AI: Privacy and Fairness in Decision Making and Learning Tasks.} \hfill{Nov 2023}\\
  {\nemph{TOC FOR FAIRNESS, Simons Collaboration on the Theory of Algorithmic Fairness}}

  \item {\bf Panelist}: {Navigating the Frontiers of Artificial Intelligence.} \hfill{Oct 2023}\\
  {\em  The Center for Politics, University of Virginia}

  \item {\bf Invited talk}: {Optimization and Learning for Science and Engineering.} \hfill{Oct 2023}\\
  {\em  Conference on Complex Systems 2023}

  \item {\bf Invited talk}: {ML for Optimization and Optimization for ML.} \hfill{Sep 2023}\\
  {\em  AI/ML Seminar Series, University of Virginia}

  \item {\bf Keynote talk}: {The Unintended Societal Effects of Privacy in Decision and Learning Tasks.} \hfill{Aug 2023}\\
  {\em  IJCAI-2023, International Workshop on Mining Actionable Insights from Social Networks}

  \item {\bf Invited talk}: {End-to-end Constrained Optimization Learning.} \hfill{Jul 2023}\\
  {\em  AC Summer School: Machine Learning for Constraint Programming}

  \item {\bf Invited talk}: {Differential Privacy for Power Systems.} \hfill{Jun 2023}\\
  {\em  DTU PES Summer School}

  \item {\bf Invited talk}: {Optimization Proxies and Differentiable Optimization for Decision Making.} \hfill{Jun 2023}\\
  {\em  MARS Seminar, Pacific Northwest National Laboratory (PNNL)}

  \item {\bf Invited talk}: {Constrained-aware Machine Learning in Energy Systems.} \hfill{Jun 2023}\\
  {\em  IEEE Power and Energy Society webinar series}

  \item {\bf Invited talk}: {Responsible AI: Privacy and Fairness in Decision and Learning Tasks.} \hfill{Apr 2023}\\
  {\em  UC San Diego}

  \item {\bf Panelist}: {ChatGPT: Charms and Challenges.} \hfill{Apr 2023}\\
  {\em  Syracuse University}

  \item {\bf Invited talk}: {Responsible AI: Privacy and Fairness in Decision and Learning Tasks.} \hfill{Mar 2023}\\
  {\em  University of Virginia}

  \item {\bf Invited talk}: {Constrained-Aware Machine Learning.} \hfill{Feb 2023}\\
  {\em  Washington University in St.~Louis}

  \item {\bf Invited talk}: {Differential Privacy for Power Systems.} \hfill{Jan 2023}\\
  {\em  Los Alamos National Lab's 5th Grid Science Winter School and Conference}

  \item {\bf Panelist}: {Algorithmic Fairness and its Intersections.} \hfill{Dec 2022}\\
  \press{https://neurips.cc/virtual/2022/tutorial/55815}
  {\em Thirty-sixth Conference on Neural Information Processing Systems (NeurIPS)}

  \item {\bf Tutorial}: {End-to-end constrained optimization learning.} \hfill{Dec 2022}\\
  \press{https://aixia2022.uniud.it/}{\em 21st International Conference of the Italian Association for Artificial Intelligence (AIxIA 2022)}

  \item {\bf Media cover}: 
  {How network pruning can skew deep learning models.} \hfill {Nov 2022}\\ 
  \press{https://www.sciencedaily.com/releases/2022/11/221102115535.htm}{{\em Science Daily}}~
  \press{https://techxplore.com/news/2022-11-network-pruning-skew-deep.html}{TechXplore}~
  \press{https://www.eurekalert.org/news-releases/970000}{AAAS EurekAlert}~

  \item {\bf Invited talk}: {Disparate Impacts in Privacy-preserving Machine Learning.} \hfill{Nov 2022}\\
  {\em Washington University in St.~Louis} 
  % {\em University of Maryland, College Park}  \hfill {Nov 2022}
  %{\em New Jersey Institute of Technology}    \hfill {Dec 2022}

  \item {\bf Tutorial}: {Decision Focused Learning.} \hfill{Oct 2022}\\
  \em{Dagstuhl seminar on Data-Driven Combinatorial Optimisation}
  
  \item {\bf Media interview}: {Privacy and Fairness in AI.} \hfill Jul/Sep 2022\\
  \press{https://news.syr.edu/blog/2022/08/03/professor-receives-award-for-outstanding-research-in-privacy-enhancing-technologies/}{Syracuse Media Report}~
  \press{https://artsci.nmsu.edu/news-events/2022/07/nmsu-alumnus-gains-international-recognition-for-research-on-privacy-and-fairness-in-ai.html}{NMSU News}
  \press{https://www.lcsun-news.com/story/news/education/nmsu/2022/09/03/nmsu-alum-gains-international-recognition-for-research-on-ai-privacy/65467086007/}{Sun News}

  \item {\bf Media interview}: {Google Scholar Research Award.} \hfill Jun 2022\\
  \press{https://news.syr.edu/blog/2022/06/22/two-professors-win-prestigious-google-research-scholar-awards/}{Syracuse Media Report}

  \item {\bf Tutorial}: {Impacts of Data Privacy and Equity on Public Policy.} \hfill {Jun 2022}\\ 
  \press{https://www.youtube.com/watch?v=ersvD5Nja98&t=8s&ab_channel=FerdinandoFioretto}{\em ACM Conference on Fairness, Accountability, and Transparency (FAccT)}

  \item {\bf Panelist}: Fostering the Use of AI for Power System Transformation. \hfill Jun 2022\\
  \press{https://www.climatechange.ai/webinars}{\em Climate Change AI}

  \item {\bf Media interview}: {NSF CAREER Award.} \hfill Jun 2022\\
  \press{https://ecs.syracuse.edu/about/news/electrical-engineering-and-computer-science-professor-ferdinando-fioretto-receives-national-science-foundation-nsf-career-award}{Syracuse Media Report}

  \item {\bf Invited talk}: End-to-end constrained deep learning optimization. \hfill Mar 2022\\
  {\em Hall of Science (Kantar.com)} 

  \item {\bf Panelist}: {AAAI-22 DC - Career Panel.} \hfill {Feb 2022}\\
  \press{https://aaai.org/Conferences/AAAI-22/doctoral-consortium-program/}{\em 36th AAAI Conference on Artificial Intelligence (AAAI)}

  \item {\bf Invited talk}: {Privacy-preserving ML and decisions-making: uses and unintended disparate effects.}   \hfill {Feb 2022}\\
  \press{https://prisec-ml.github.io/}{\em PriSec-ML (virtual seminars)}

  \item {\bf Media interview}:  {AI for Climate Change.} \hfill {Dec 2021}\\ 
  \press{https://www.rainews.it/tgr/puglia/notiziari/index.html?/tgr/video/2021/12/ContentItem-4aae6540-8707-4a9f-8b6d-3ec515470539.html}
  %https://www.raiplay.it/programmi/playdigital}{RaiPlay} 
  {RaiNews}

  \item {\bf Popular Media Report}: ISSNAF Young Investigator Award. \hfill {Nov 2021}\\
  \press{https://www.lavocedinewyork.com/people/nuovo-mondo/2021/12/10/issnaf-premia-i-migliori-giovani-ricercatori-italiani-in-usa-e-chiude-un-anno-di-nuovi-progetti/}{New York Voice}~
  \press{https://www.aise.it/comunit\%C3\%A0/issnaf-premia-i-migliori-giovani-ricercatori-italiani-negli-usa/169636/}{AISE}~
  \press{https://www.ilmattinodifoggia.it/news/cultura/56658/nando-fioretto-di-san-severo-tra-i-finalisti-del-premio-ai-giovani-scienziati-italiani-del-nord-america.html}{{\em Il Mattino}}~
  \press{https://startupitalia.eu/166650-20211126-dallai-alla-letteratura-i-ricercatori-italiani-che-innovano-in-nord-america}{{\em StartupItalia}}~
  \press{https://citymilano.com/2021/11/25/dalla-sostenibilita-globale-allinnovazione-nelle-scienze-umane-ecco-i-migliori-giovani-ricercatori-italiani-in-nord-america/}{{\em Zox}}~
  \press{https://www.puglianews24.eu/dalla-puglia-ad-harvard-per-studiare-i-geni-e-combattere-la-leucemia-62441.html}{{\em PugliaNews}}
  
  \item {\bf Invited talk}:  {Deep Constraint Learning: Applications and Privacy Considerations.} \hfill {Nov 2021}\\
  \press{https://www.youtube.com/watch?v=eyKhU3GzdYA&ab_channel=ISSNAF-ItalianScientistsandScholarsinNorthAmericaFoundation}{\em Italian Scientists \& Scholars in North America Foundation} 
  
  \item \textbf{Plenary Keynote talk}: Constraint-based Differential Privacy. \hfill Oct 2021\\
  \press{https://cp2021.lirmm.fr/submissions/1002}{\em The International Conference on Principle and Practice of Constraint Programming (CP 2021)}, 
  
  \item {\bf Popular Media interview}: {Deep Learning for Engineering Applications.} \hfill {Nov 2021}\\ 
  \press{https://blum.vision/?lang=en}{{\em Blum News}} 

  \item \textbf{Invited talk}: Privacy-Preserving Machine Learning: Uses and Unintended Disparate Effect. \hfill Sep 2021\\
  {\em ASPI Seminar (Syracuse University)} 
  
  \item \textbf{Invited talk}: Differential Privacy and Machine Learning. \hfill May 2021\\
  {\em SUPA ECS workshop for High School Teachers}
  
  % \item {\it Invited Talk, REsearch Exposure in Socially Relevant Computing}
  % \hfill {Apr 2021}

  \item {\bf Invited talk}: Deep Constraint Learning for Critical Engineering Systems. \hfill {Nov 2020}\\
  \press{https://www.youtube.com/watch?v=eyKhU3GzdYA&ab_channel=ISSNAF-ItalianScientistsandScholarsinNorthAmericaFoundation}{\em Italian Scientists \& Scholars in North America Foundation} 
  
  \item {\bf Tutorial}: {Tutorial on Multiagent Optimization.} \hfill {Feb 2020}\\ 
  \press{https://www2.isye.gatech.edu/~fferdinando3/cfp/AAAI20/}{\em AAAI Conference on Artificial Intelligence (AAAI 2020)} 
  
  \item {\bf Media cover}: {Multiagent Systems.} \hfill{Feb 2020}\\
  \press{https://www.agendadigitale.eu/cultura-digitale/i-sistemi-multiagente-cosi-governiamo-lintelligenza-artificiale/}{NetworkDigital360} 

  \item {\bf Invited talk}:  Privacy-Preserving Artificial Intelligence. \hfill {Jun 2019}\\
  {\em University of Parma (CS Dept)} 

  \item {\bf Tutorial}: {Tutorial on Multiagent Optimization for IoT Applications.} \hfill {May 2019}\\ 
  \press{}{\em International Conference on Autonomous Agents and Multiagent Systems (AAMAS 2019)} 

  \item {\bf Invited talk}: Differential Privacy for AI Applications\\
  {\em University of Southern California - Information Sciences Institute.} \hfill {Jan 2019}\\
  {\em Michigan State University.} \hfill {Feb 2019}

  \item {\bf Invited talk}: Privacy Preserving Artificial Intelligence\\
  {\em Syracuse University.} \hfill {Feb 2019}\\
  {\em Drexel University.} \hfill {Feb 2019}\\
  {\em University of Arkansas.} \hfill {Feb 2019}\\
  {\em Colorado State University.} \hfill {Mar 2019}\\
  {\em University of Connecticut.} \hfill {Mar 2019}
  % {\em University of New Mexico} \hfill {Mar 2019}

  %{\em Missouri University of Science and Technology} \hfill {Feb 2019}
  % {\em University of Denver} \hfill {Jan 2019}

	% \item {\it AI Lab Seminar}, University of Michigan (EECS Dept)
	% \hfill {Aug 2018}

   % \item {\it Invited Presentation}, 
	% Privacy in Machine Learning and Artificial Intelligence Workshop 
	% (ICML/IJCAI/AAMAS 2018)
	% \hfill {Jun 2018}

	% \item {\it AI Seminar}, University of Southern California Information Sciences Institute (USC ISI)
	% \hfill {Mar 2018}

	% \item {\bf Seminar}: Differential Privacy for AI Applications\\
	% {\em New Mexico State University} \hfill {Mar 2018}

	\item {\bf Tutorial}: {Tutorial on Constrained Multi-agent Optimization.} \hfill {Feb 2018}\\
	\press{https://www2.isye.gatech.edu/~fferdinando3/cfp/AAAI20/}{\em AAAI Conference on Artificial Intelligence (AAAI 2018)} 
  	

	\item {\bf Plenary Keynote talk}: Distributed Constraint Optimization for Smart Energy Networks. \hfill {Nov 2017}\\
    {\em Italian Conference on Artificial Intelligence (AI*IA 2017)}
	

	\item {\bf Invited talk}: Distributed Constraint Optimization\\
	{\em Delft University (TU Delft).} \hfill {Apr 2016}\\
 	{\em University of Udine.} \hfill {Apr 2016} \\ 
	{\em New Mexico State University.} \hfill {Mar 2016}
	
	\item {\bf Invited talk}: Large Neighboring Search for Distributed Constrained Optimization. \hfill {Mar 2016}\\
	{\em Ben-Gurion University of the Negev}
\end{itemize}
