\documentclass[times, 10pt]{article}
%\usepackage{times}
\usepackage{fullpage}
\usepackage{etaremune}
\usepackage{fancyhdr}
\usepackage{color}
\usepackage{ifthen}
\usepackage{paralist}
\usepackage{enumitem}

\newcommand{\emptymemo}[1]{\noindent\fbox{\begin{minipage}[b]{1.0in}#1\end{minipage}}}
\newcommand{\newitemize}[2]{\newcounter{#1}\begin{list}{\arabic{#1}}{\usecounter{#1}\addtolength{\itemsep}{-0.60\baselineskip}\addtolength{\leftmargin}{-0.00\leftmargin}}#2\end{list}}

\newcommand{\belist}{\begin{list}{\labelitemi}{\itemsep 0.00em \parsep 0.00em \topsep 1.20em}} 
\newcommand{\enlist}{\end{list}}

\newcommand{\belistb}{\begin{list}{\labelitemi}{\itemsep 0.25em \parsep 0.00em \topsep 1.20em \parskip -1.00em}} 
\newcommand{\enlistb}{\end{list}}

\def\beginTitleList{\begin{list}{}{\topsep=0pt \itemsep=10pt \parsep=0pt \leftmargin=0pt}}
\def\endTitleList{\end{list}}

\def\procAAMAS{\emph{Proceedings of International Conference on Autonomous Agents and  Multiagent Systems (AAMAS)}}
\def\procAAAI{\emph{Proceedings of the AAAI Conference on Artificial Intelligence (AAAI)}}
\def\procIJCAI{\emph{Proceedings of the International Joint Conference on Artificial Intelligence (IJCAI)}}
\def\procCP{\emph{Proceedings of the International Conference on Principles and Practice of  Constraint Programming (CP)}}
\def\procECAI{\emph{Proceedings of the European Conference of Artificial Intelligence (ECAI)}}
\def\procISIAM{\emph{International Symposium on Artificial Intelligence and Mathematics (ISAIM)}}
\def\procCPAIOR{\emph{In Proceedings of the International Conference on the Integration of Constraint Programming, Artificial Intelligence, and Operations Research (CPAIOR)}}
\def\procPADL{\emph{Proceedings of the Practical Aspects of Declarative Languages (PADL)}}
\def\procPRIMA{\emph{Proceedings of the International Conference on Principles and Practice of Multi-Agent Systems} (PRIMA)}
\def\procCMSB{\emph{Proceedings of the Computational Methods in System Biology (CMSB)}}
\def\JAIR{\emph{Journal of Artificial Intelligence Research} (JAIR)}


\setlength{\parskip}{0pt}

\newboolean{forPnT}
\setboolean{forPnT}{false} % boolvar=true or false

\newcommand{\pnt}[1]{
  \ifthenelse {\boolean{forPnT}}{#1}

}

\sloppy

 \special{! /pdfmark where
 {pop} {userdict /pdfmark /cleartomark load put} ifelse
 [ /Author (Ferdinando Fioretto)
 /Title (Ferdinando Fioretto - Curriculum Vitae)
 /Subject ()
 /Keywords ()
 /DOCINFO pdfmark}

\pagestyle{fancy} \lhead{Ferdinando Fioretto} \cfoot{\thepage}
\rhead{Short CV}

%\headheight 0.2in
\headsep 0.3in

\begin{document}

\thispagestyle{empty}

\vspace*{-0.50in} \noindent {\LARGE Ferdinando Fioretto \hfill Short CV} \line(1,0){475}

\begin{tabular}[t]{r}
\hspace{2.6in} 
Department of Electrical Engineering \& Computer Science \\
%College of Engineering \& Computer Science \\
Syracuse University \\
%223 Link Hall, 
Syracuse, NY 13244\\
%Phone: (575) 621-5948 \\
\texttt{ffiorett@syr.edu} \\
\texttt{http://nandofioretto.com}
\end{tabular}

\subsection*{\sc Professional Preparation:}
% \begin{list}{$\bullet$}{\topsep=1pt \itemsep=1pt     \parsep=0pt}

\begin{tabular}{l l l l l }
$\bullet$ & University of Parma, Italy & Computer Science 
&\phantom{a}B.S.E. & {2009} \\ 
$\bullet$ & New Mexico State University, USA & Computer Science 
&\phantom{a}M.S. & {2011} \\ 
$\bullet$ & University of Udine, Italy & Computer Science 
&\phantom{a}Ph.D. & {2016} \\
$\bullet$ & New Mexico State University, USA & Computer Science 
&\phantom{a}Ph.D. & {2016} \\ 
\end{tabular}


\subsection*{\sc Appointments:}

\belist
	\item
	{\em Assistant Professor}, Syracuse University, Syracuse, NY \hfill{2020 -- Current}
	\item Postdoc, Georgia Institute of Technology, Atlanta, GA 
	\hfill{2018 -- 2019}
	\item Postdoc, University of Michigan, Ann Arbor, MI 
	\hfill{2018 -- 2020}	
\enlist



\subsection*{\sc Five Most Closely Related Products:}

\begin{enumerate}[leftmargin=*, parsep=2pt, itemsep=2pt, topsep=2pt]
\item 
	James Kotary, Ferdinando Fioretto, Pascal Van Hentenryck.
	``Learning Hard Optimization Problems: A Data Generation Perspective'. NeurIPS 2021.

% \item 
% 	Ferdinando Fioretto, Lesia Mitridati, Pascal Van Hentenryck ``Differential Privacy for Stackelberg Games''. 
%   	IJCAI, 2020.

\item 
	Ferdinando Fioretto, Terrence W.K.~Mak, and Pascal Van Hentenryck.
	``Predicting AC Optimal Power Flows: Combining Deep Learning and Lagrangian Dual Methods".
  	AAAI, 2020.

% \item 
% 	Ferdinando Fioretto, Terrence W.K. Mak, Federico Baldo, Michele Lombardi, Pascal Van Hentenryck 
% 	``A Lagrangian Dual Framework for Deep Neural Networks with Constraints''. 
% 	\emph{ECML}, 2020. 

\item
	Ferdinando Fioretto and Pascal Van~Hentenryck.
	``Privacy-Preserving Federated Data Sharing".
  	AAMAS, 2019.

\item
	Ferdinando Fioretto, Enrico Pontelli, and William Yeoh.
	{``Distributed Constraint Optimization Problems and Applications: A Survey"}.
	JAIR, 61, pages 623--698, 2018. 

\item 
	Ferdinando Fioretto,  William Yeoh, and Enrico Pontelli. 
	{``A Multiagent System Approach to Scheduling Devices in Smart Homes"}.
	AAMAS, 2017. 

	% \item 
	% Ferdinando Fioretto, William Yeoh, and Enrico Pontelli.
	% {``Multi-Variable Agent Decompositions for DCOPs"}. 
	% AAAI, 2016.
\end{enumerate}


\subsection*{\sc Synergistic Activities:}

\begin{itemize}[leftmargin=*, parsep=2pt, itemsep=2pt, topsep=2pt]
\item \textbf{Selected Awards}: ACP Early CAREER Research Award (2021); NeurIPS Outstanding Reviewer Award (2021); Young Investigator Award, Finalist, ISSNAF (2020); Best Paper Award, IEEE Transaction of Power System (2020); Differentially Private Temporal Map Challenge Award (2020); Best AI Dissertation Award - IA*AI (2017); Most Visionary Workshop Paper Award - AAMAS (2017); Best Student Paper Award - CMSB (2013); Top 5\% Graduate student honor’s cord - NMSU (2016).

\item \textbf{Selected Symposium/Workshop/Track Co-Chair}: AAAI Workshop on Privacy Preserving Artificial Intelligence (2020-2022); AAAI Workshop on Machine Learning for Operations Research (2022); Multiagent and Parallel CP track, International Conference on Principles and Practice of Constraint Programming (2018, 2019); International Workshop on Optimization in Multi-Agent Systems (2018-2021); CP cluster, International Symposium of Mathematical Programming (2018).

\item \textbf{Selected Senior Program Committee Member/Area Chair}: AAAI Conference on Artificial Intelligence (2021-2022); International Conference on Principles and Practice of Constraint Programming (2018, 2019); International Joint Conference on Artificial Intelligence (2021-2022);
% •	Program Committee Member: AAAI Conference on Artiﬁcial Intelligence (2018, 2019); European Con-ference on Artiﬁcial Intelligence (2016–2018); European Conference on Machine Learning (2020); Inter-national Conference on Autonomous Agents and Multiagent Systems (2017–2021); International Joint Conference on Artiﬁcial Intelligence (2016–2020); Neural Information Processing Systems (2020).
\end{itemize}

% \subsection*{\sc List of Collaborators:}
% \begin{itemize}[leftmargin=*, parsep=0pt, itemsep=0pt, topsep=2pt,partopsep=0pt]
% 	\item {\bf Post-doctoral Advisor} 
% 	Pascal Van Hentenryck (Georgia Institute of Technology)
% 	\item {\bf Ph.D.~Advisors} 
% 	Enrico Pontelli (New Mexico State University); 
% 	Agostino Dovier \mbox{(University of Udine)}
% 	\item {\bf Collaborators} 
% 	%Eric Boyd (University of Michigan)
% 	Rina Dechter (University of California, Irvine),
% 	Christopher Kiekintveld	(University of Texas, El Paso),
% 	Sven Koenig (University of Southern California),
% 	T.~K.~Satish Kumar (University of Southern California),
% 	Chansoo Lee (Google),
% 	Michele Lombardi (University of Bologna), 
% 	Terrence W.~K.~Mak (Georgia Institute of Technology),
% 	Lesia Mitridati (Georgia Institute of Technology), 
% 	Alessandro Dal Pal\'{}u (University of Parma),
% 	Satish J.~Ranade (New Mexico State University),
% 	Tran Cao Son (New Mexico State University)
% 	William Yeoh (Washington University in St.~Louis),
% 	Makoto Yokoo (Kyushu University),
% 	Roie Zivan (Ben-Gurion University).
% \end{itemize}

\end{document}
